Manuscript_Github_Pchabaudi_pir

### 2021-03-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
figure 4 only RMT

cir_plot <- twentyfour_ct_comb %>% 
  filter(Geneid %in% cir_housekeeping_id) %>%
  melt(id.vars = 'Geneid', 
       variable.name = 'sample', 
       value.name = 'tpm') %>% 
  mutate(
    stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = ''),
    transmission = str_split_fixed(sample, pattern = '_', n = 3)[,1],
    diff_count = str_split_fixed(sample, pattern = '_', n = 4)[,3],
    time = str_split_fixed(sample, pattern = '_', n = 3)[,2],
    subfam = cir_clade_info$clade[match(Geneid, cir_clade_info$Geneid)]
  ) %>% 
  mutate(subfam = ifelse(is.na(subfam), 'ref', subfam)) %>% 
  filter(!(time %in% c('sch.culture', 
                       'Unknown'))) %>% 
  mutate(subfam = str_replace(subfam, 
                              'ancestral',
                              'a')) %>% 
  mutate(
    subfam = interaction(
      transmission,
      forcats::fct_shift(
        relevel(
          as.factor(subfam),
          ref = 'ref')
      ),
      sep = '_',
      lex.order = TRUE
    )
  )
#Need to add the transmission name to the subfam so that they are ordered correctly.
# Need to move 'ref' factor to the start of the subfam, then shift the factor levels to the 'left' (so now
# ref is at the end) ensuring that the 'ref' genes are at the end of the graph for each transmission type.

@@

cir_plot_order <- cir_plot %>% 
  filter(time == '14h',
         transmission == 'RMT') %>% 
  arrange(desc(tpm))

@@

  lapply(unique(cir_plot_filter$transmission), 
         function(transmission_method){

           cir_plot_filter <- filter(cir_plot_filter, 
                              transmission %in% transmission_method)

@@

           grid.newpage()
           grid.draw(g)
         })

>>>>

cir_plot <- twentyfour_rMT %>% 
  filter(Geneid %in% cir_housekeeping_id) %>%
  melt(id.vars = 'Geneid', 
       variable.name = 'sample', 
       value.name = 'tpm') %>% 
  mutate(
    stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = ''),
    diff_count = str_split_fixed(sample, pattern = '_', n = 4)[,2],
    time = str_split_fixed(sample, pattern = '_', n = 3)[,1],
    subfam = cir_clade_info$clade[match(Geneid, cir_clade_info$Geneid)]
  ) %>% 
  mutate(subfam = ifelse(is.na(subfam), 'ref', subfam)) %>% 
  filter(!(time %in% c('sch.culture', 
                       'Unknown'))) %>% 
  mutate(subfam = str_replace(subfam, 
                              'ancestral',
                              'a'))

#Need to add the transmission name to the subfam so that they are ordered correctly.
# Need to move 'ref' factor to the start of the subfam, then shift the factor levels to the 'left' (so now
# ref is at the end) ensuring that the 'ref' genes are at the end of the graph for each transmission type.

@@

cir_plot_order <- cir_plot %>% 
  filter(time == '14h') %>% 
  arrange(desc(tpm))

@@

@@

           grid.newpage()
           grid.draw(g)
